### 2018-04-11 paper.Rmd
added versioning details and annotation coverage infromation

<!-- [[mention using XML childes representation]] -->

@@

<!-- [[Details of extraction]] -->
<!-- [[Details of testing: Why trust our parse over your in-house library? CLAN TESTING DETAILS - also mention versioning as a reason to trust]] -->

@@

<!-- Potentially put some R code to show easy it is to access previous versions? -->

To reflect changes in the CHILDES database as new corpora are added or previous annotations revised, we produce a new versioned parse of the complete database every 6 months. By default, users connect to the most recent version. To support reproduction of results with previous versions of the database, we provide access to hosted versions through our `childesr` API so that researchers can refer to specific releases. Compressed .sql files are available for download.

### Current annotation coverage

<!-- [[ How are we handling the long tail of tiers? first priority is lexical statistics & morphology, but there's other stuff too]].  -->

<!-- no media links currently, no timing information -->

<!-- this stuff could be added at some point without changing format -->

>>>>

@@

<!-- [[Details of extraction]] -->
<!-- [[mention using XML childes representation]] -->
<!-- [[Details of testing: Why trust our parse over your in-house library? CLAN TESTING DETAILS - also mention versioning as a reason to trust]] -->

@@

The content of CHILDES changes as additional corpora are added or transcriptions are updated; currently, these changes are not systematically tracked.
Here we introduce a simple versioning system by proucing a new complete parse of the current state of CHILDES every 6 months.
Users interact with the most recent version of the database available by default. 
To support reproduction of results with previous versions of the database, we continue to host recent versions (up to the last 6 versions) through our `childesr` API so that researchers can run analyses against specific versions of the database.
<!-- Potentially put some R code to show easy it is to access previous versions? -->
For versions more than three years old, users have the options of downloading compressed .sql files and serving them with a local installation of MySQL server.
<!-- How easy is it to implement versioning in the Shiny apps?-->

### Current Annotation Coverage

The current implementation of childes-db emphasizes the computation of lexical statistics, and consequently focuses on reproducing the words, utterances, and speaker information in CHILDES.
We have yet to parse and make available the following information:

- Sparsely annotated tiers, e.g. phonology (`%pho`) and situation (`%sit`)
- Media links, including timing information
- compound word markers, indicated with underscores ("green_eggs_and_ham")
- Tone direction and stress
- Filled pauses 
- Reformulations, word revision, and phrase revision, e.g. <what did you> [//] how can you see it ?
- paralinguistic material, e.g. [=! cries]

We will prioritize the addition of these additional information sources in response to community feedback;
extending coverage to the above information sources will not require changes to the existing database schema.
